Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-05 paper/paper.tex
Added abstract to the paper.

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
Tabnabbing is a phishing technique that attempts to change the look and design of a tab when the user is not currently viewing it so that when the user returns, they will find a seemingly trustworthy form or page requesting their credentials and information.  
This attack utilizes the user's trust of recently viewed tabs, and the perceived immutability of out-of-focus tabs.
Tabnabbing attacks change the appearance of tabs by using JavaScript or the HTML meta tag.  
Previous attempts of addressing tabnabbing have relied upon detecting tabnabbing after it has occurred.  
Detecting whether a page has changed with the malicious intent of tabnabbing is a complex problem that is difficult to solve without large amounts of processing or false positives.  
The authors of this paper investigated and developed a preemptive measure to prevent tabnabbing attacks from occurring.  
The resulting Chrome browser extension, Nabi, prevents any JavaScript or HTML meta tags from running in inactive tabs outside of a trusted whitelist.
\end{abstract}
